\section{Application and Data Architecture}
< Complete logical or physical model is expected. Diagrams/Tools that may be provided in this section include Component Diagram, ER Diagram, Class Diagram (with complete inheritance, composition, and association details), Activity Diagram, Decision Table etc. All these diagrams should have more details than the details provided in Phase 1 of the SDP. Research based projects may provide complete design of the proposed system. Describe each diagram briefly.>

\section{Component Interactions and Collaborations}
<Provide interactions and collaborations between your system components/processing units. Diagrams/Tools that may be provided in this section include Design Level Sequence Diagram, Collaboration Diagram, Event Traces, Detailed DFD, Activity Diagram etc. All these diagrams should have more details than the details provided in Phase 1 of the SDP. Describe each diagram briefly.>

\section{System Architecture}
<Provide the technical architecture of your system. Include a high-level architecture diagram that highlights major subsystems and components.>

\section{Architecture Evaluation}
<Describe the reason(s) behind the decision related to selection of infrastructure/technology used. Discuss pros and cons of the selected technology/infrastructure and the alternative technology/infrastructure. For example why have your group selected a particular API from a list of APIs? Why have your group preferred a particular framework over an alternative framework.>

\section{Component-External Entities Interface}
< Express the communication between components of your system and components of other systems such as NADRA system, bank, credit card verification system, third party multi game server etc. Use appropriate diagram to show the interaction in a better manner.>

\section{Screenshots/Prototype}
\subsection{Workflow}
<Describe complete workflow of your system. Swim-lane diagram may be used. This section should be an improved version of the section presented in previous phases>

\subsection{Screens}
< Include all screenshots of your complete software application’s graphical user interface.>

\section{Other Design Details}
<Describe all design details not covered in previous sections. Add subsections as required. There can be details regarding Research Oriented, Game Oriented, or Hardware based projects that have not been covered in this document before, those details can be provided in this section. For example research based projects may use this section to present their results and analysis; hardware based projects may use this section to describe interface dependencies and issues etc.>